%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

%\cvsection{Programmering och program}
\cvsection{Skills}


%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvskills}

%------------------------------------------------

\cvskill
{Python:}
{very good knowledge. Familiar with jupyter, numpy, scikit-learn.}

\cvskill
{C++:}
{very good knowledge, was the primary language during my PhD.}

\cvskill
{pandas:}
{basic knowledge, occasional use. The concepts are very familiar as I worked with data structured \newline similarly to DataFrames.}

\cvskill
{bash/terminal:}
{have used a terminal daily during my PhD.}

\cvskill
{Docker:} 
{good knowledge. I set up an exercise for teaching purposes using Docker.}

\cvskill
{git and svn:}
{good knowledge. Code versioning was crucial when working in a large international collaboration.}

\cvskill
{vim:}
{very good knowledge.}

\cvskill
{LaTeX:}
{very good knowledge. Have typeset documents in LaTeX since my undergraduate days.}

\cvskill
{Statistics:} 
{expert knowledge, mostly of frequentist methods.}

\cvskill
{Mathematical/numerical}{}
\cvskill{modelling:}
{very good knowledge: Highly familiar with Monte Carlo simulations.}
%\cvskill
%{}
%{}
%{ har erfarenhet av fr{\aa}n doktorandtiden. V{\"a}lbekant med Monte-Carlo-simuleringar.}

\cvskill
{Machine learning:}
{good knowledge. Experience of artificial neural networks and decision trees.}

\cvskill
{Languages:}
{Swedish: native speaker. English: fluent in speaking and writing.}

\cvskill
{Driver's licence:}
{B.}
%------------------------------------------------

%\cvskill
%{Spr{\aa}k} % Category
%\begin{cvitems}
%\item Svenska: Modersm{\aa}l. % Skills
%\item Engelska: Flytande i tal och skrift. % Skills
%\end{cvitems}
%------------------------------------------------

\end{cvskills}