%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{../awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\usepackage[utf8]{inputenc}
\usepackage[swedish]{babel}

\geometry{left=3.5cm, top=1.5cm, right=3.5cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-skyblue} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\input{../header}

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{Junior Algorithm Developer}{} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

%\lettertitle{------------------------------------------------------------------------------------------------------------------------------------------------} % The title of the letter

\letteropening{\vspace{0.8cm}Dear Samuel, Tobii,} % How the letter is opened

\letterclosing{Best regards, \\ Edvin} % How the letter is closed

%\letterenclosure[Bifogat]{CV} % Any enclosures with the letter

%\makecvfooter{\today}{Claud D. Park~~~Â·~~~Cover Letter}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
  
%----------------------------------------------------------------------------------------

\begin{document}
\sloppy % use \sloppy to make sure words don't extend into margin

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}
\vspace{.2cm}
%------------------------------------------------
I was truly inspired by Peter Schef when he came to my previous workplace to talk about life and work at Tobii. 
It was exciting to see how eye tracking applications span from assistive technology to research and gaming.
It certainly seems true that only imagination limits its use.
I would really like to contribute to overcome the challenges in making the technology work broadly, at scale.


I recently graduated from the Royal Institute of Technology (KTH) in Stockholm where I did research as part of a large international collaboration based at the particle physics laboratory CERN outside Geneva.
%Part of a group of about 25 people we carried out a measurement of the newly discovered Higgs particle, by producing such particles in the proton collisions made by the Large Hadron Collider.
My main project concerned a measurement of one of nature's fundamental particles (the Higgs boson).
This was done together with my research group by filtering the experiment's large dataset of proton collisions for this particle. %collected by the experiment, . % and solving problems arising in the process of understanding the data.
%The research is largely based on analysing ATLAS' large dataset and solving problems arising in the process of understanding the data.
For two years I led the effort to estimate one particular source of contamination of the data, the estimation of which was crucial to reach publication. 
The contamination was special in that it's not easily estimated using standard simulations–more unconventional, data-driven solutions had to be found.
In this effort I developed a strong analytical skill set and a creative mind. % to overcome such. %EXEMPEL?
%Advanced statistical methods are used to extract the most out of the data.
The data analysis was performed in C++ and python, in which I have acquired strong skills. %  in C++ and to some extent Python.
I learned a lot about advanced statistical methods which were applied to extract the most out of the data.
In addition, I gained experience with multivariate and machine learning techniques, which would come in useful for this position. % are used
For example, I worked on evaluating the robustness of the artificial neural networks used to classify the pixel clusters (images) input to particle track formation.
In the main project, boosted decision trees were trained to identify data containing the signal particle.  %based on data characteristics.
%However, I am mostly glad for the {\it statistical thinking} or attitude I feel I have developed--in my opinion, understanding data relies on having the right mindset, more so than being able to apply a series of methods from a recipe.
%This way of thinking is useful in all situations in which one deals with data.

Having worked in a large collaboration I realise the importance of good coding practises and version control (I am comfortable using git).
I think this will be an asset for the job as an algorithm developer, like my interest in software: while many I worked with tried to move as quickly as possible to results, I enjoyed spending a little extra time on making code more elegant and stable.
Furthermore, I have come to appreciate the benefits of automating–more often than not one will find the need to repeat a task.

My colleagues would describe me as positive and stress resilient, capable and with a will to understand.
When faced by a new, difficult problem, I see it as a challenge and an opportunity to learn new things rather than getting scared or uncomfortable. 
%To exemplify, I was during my PhD often faced with open-ended problems. % was it is not obvious which solution is the best.
%For example, I learned Docker when given
For example, I was given the job to develop and set up a laboration exercise for teaching purposes. 
After considering different alternatives, I realised a solution based on Docker (which I then educated myself in) would be a neat way to eliminate the need for software installation on the student side.

I hope I with this letter have convinced you that I am worth considering, and that I will hear from you shortly!

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}